Kronos \& Krios: Evidence for accretion of massive, rocky planetary system in a sun-like pair

### 2017-06-05 paper/ms.tex
Add keywords
Edit the abstract

\begin{abstract}
  We report and discuss the discovery of a comoving pair of bright solar-type
  stars, HD~240430 and HD~240429, with a significant difference in their chemical
  abundance patterns.
  The two stars are co-spatial ($|\Delta \bs{x}| < XX~\pc$) at a distance of
  $r\approx 100~\pc$ with nearly identical three-dimensional velocities
  ($|\Delta \bs{v}| < XX~\kms$ with 95\% confidence), as inferred from \gaia\
  \tgas\ proper motions and high resolution radial velocity measurements.
  Both stars are young with ages $\approx$$500~{\rm Myr}$ as estimated from
  their lithium abundances, favoring the idea that they were born together and
  are or were recently a bound, wide binary system.
  However, the metallicities and chemical abundances of refractory
  elements in the two stars are very different, challenging this simple picture.
  In order to reconcile the seemingly contradictory observations,
  we consider scenarios in which the pair is unrelated despite
  its current spatial and kinematic configuration, and
  those in which the pair formed together but may now have different chemistry.
  In the latter, we consider the possibility that the more metal-rich of the two,
  \bizarreone, accreted $\approx$10's of Earth masses of protoplanetary, rocky material,
  selectively enhancing the refractory elements.
  Direct-imaging and precision radial velocity follow-up to study the existence
  or properties of planetary systems around these stars would help distinguish
  these scenarios.
\end{abstract}

@@

\begin{figure}[htpb]
  \centering
  \includegraphics[width=0.95\linewidth]{TcRank_deltaXH_concise.pdf}
  \caption{Abundance difference of \bizarreone-\sunanalog\ pair
    ranked by the condensation temperature of elements for solar composition gas
    from \citealt{2003ApJ...591.1220L}.
    The condensation temperature may be read from the gray line and right y-axis.
    We show three wide binary systems selected from the literature:
    HD~20782/1 (\citealt{Mack:2014aa}, $\feh\approx0$),
    XO-2N/S (\citealt{Biazzo:2015aa}, $\feh\approx0.35$),
    and WASP-94AB (\citealt{Teske:2016aa}, $\feh\approx0.3$).
    Locations of elements with at least one measurement from any study
    are indicated by a vertical line and its symbol.
    Note that often multiple values are reported for one element corresponding
    to different ionization states in equivalent width analyses.
    No other pair studied so far were shown to have such large difference
    in metallicity or sharp contrast between (moderately-)volatile and
    refractory elements as \bizarreone-\sunanalog.
  }
  \label{fig:relabun_tcrank}
\end{figure}

>>>>

\begin{abstract}
  We report and discuss the discovery of a comoving pair of bright solar-type
  stars, HD~240430 and HD~240429, with a significant difference in their
  chemical abundances.
  The two stars are separated $0.6$~pc at a distance of
  $r\approx 100~\pc$ with nearly identical three-dimensional velocities,
  %($|\Delta \bs{v}| < XX~\kms$ with 95\% confidence),
  as inferred from \gaia\ \tgas\ parallaxes and proper motions, and
  high-resolution radial velocity measurements.
  Their stellar parameters determined from high-resolution KECK spectra
  indicate that both stars are $\sim 4$~Gyr old,
  yet both stars show high surface \elem{Li} abundance considering their ages.
  Moreoever, the more metal-rich of the two, HD~240430, shows an enhancement of
  refractory ($\Tcondens>1200$~K) elements by $\approx 0.2$~dex but not as
  large enhancement of (moderately) volatile elements ($\Tcondens<1200$~K; \elem{C},
  \elem{N}, \elem{O}, \elem{Na}, and \elem{Mn}):
  this is the largest and the most significant difference found in
  wide binary pairs yet.
  The proximity in phase space and ages between the two stars suggests that
  they formed together with the same composition, at odds with the observed
  differences in metallicity and abundance patterns.
  In order to reconcile the seemingly contradictory observations, we suggest
  that the star recently accreted $\approx 20$~\mearth\ of rocky material after
  birth selectively enhancing the refractory elements in its surface and
  convective envelope.
  The other star, HD~240429, may also have had a similar accretion event given
  its high surface \elem{Li} abundance but of much smaller amount
  ($\approx 4$~\mearth).
  Follow-ups to study the existence and properties of the planetary systems
  around these stars will help illuminate more on planet-star interactions.
\end{abstract}

\keywords{
  binaries: visual
  ---
  planet-star interactions
  ---
  stars: abundances
  ---
  stars: formation
  ---
  stars: individual (HD~240430, HD~240429)
  ---
  stars: solar-type
}

@@

\begin{figure}[htpb]
  \centering
  \includegraphics[width=0.95\linewidth]{TcRank_deltaXH_concise.pdf}
  \caption{Abundance difference of \bizarreone-\sunanalog\ pair
    ranked by the condensation temperature of elements for solar composition gas
    from \citealt{2003ApJ...591.1220L}.
    The condensation temperature may be read from the gray line and right y-axis.
    We show three wide binary systems selected from the literature:
    HD~20782/1 (\citealt{Mack:2014aa}, $\feh\approx0$),
    XO-2N/S (\citealt{Biazzo:2015aa}, $\feh\approx0.35$),
    and WASP-94AB (\citealt{Teske:2016aa}, $\feh\approx0.3$).
    Locations of elements with at least one measurement from any study
    are indicated by a vertical line and its symbol.
    Note that often multiple values are reported for one element corresponding
    to different ionization states in equivalent width analyses.
    No other pair studied so far were shown to have such large difference
    in metallicity or sharp contrast between (moderately) volatile and
    refractory elements as \bizarreone-\sunanalog.
  }
  \label{fig:relabun_tcrank}
\end{figure}
